\huge Tor's Usability for Censorship Circumvention

### 2016-04-07 pets2017-paper/pets2017-paper.tex
add new figures

Although Tor ~/cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

@@

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isa (?), Georg (?), and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}

>>>>

Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
using it as one, since Tor's role as a proxy to anonymize
people also worked to circumvent censorship. Now, circumventing censorship is a
common use case for Tor, and current censorship circumvention methods are
incorporated into Tor, making it a viable censorship circumvention tool even in the face
of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool.

@@

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{bridge-screens.pdf} 
		\caption{bridge screens} 
\end{figure*}

\begin{figure*}[t]
	\centering
		\includegraphics[width=1.0\textwidth]{proxy-screens.pdf} 
		\caption{proxy-screens} 
\end{figure*}

@@

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
